%! Author = Andrea
%! Date = 24/01/2024

% Preamble
\documentclass[twoside, english]{sapthesis}

% Packages
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{subcaption}
\graphicspath{{./images/}}
\usepackage{dirtytalk}
\usepackage{color}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}


\title{Keyrtual: A Lightweight Mixed Reality Musical \\Keyboard For Smartphone}
\author{Andrea Princic}
\IDnumber{1837592}
\courseorganizer{Facoltà di Ingegneria dell'Informazione, Informatica e Statistica}
\course{Computer Science}
\AcademicYear{2023/2024}
\copyyear{2024}
\advisor{Prof. Luigi Cinque}
\authoremail{princic.1837592@studenti.uniroma1.it}
\thesistype{Master thesis}
\examdate{October 22, 2024}
\examiner{Paola Velardi}
\examiner{Luigi Cinque}
\examiner{Daniele Friolo}
\examiner{Fabio Galasso}
\examiner{Marco Raoul Marini}
\examiner{Eugenio Nerio Nemmi}
\examiner{Salvatore Pontarelli}

\setcounter{secnumdepth}{2}
\newcommand{\algorithmautorefname}{Algorithm}


% Document
\begin{document}

	\frontmatter
	\maketitle

	\setcounter{tocdepth}{2}
	\tableofcontents

	\mainmatter

	\begin{abstract}
		Hand gesture recognition has become a critical area of study,
		particularly with the increasing prevalence of virtual and augmented reality technologies.
		This thesis presents the development of Keyrtual,
		a lightweight mixed reality musical keyboard application for smartphones.
		The application allows users to play a virtual musical keyboard by
		recognizing hand gestures over a physical keyboard drawn on paper.
		Leveraging the capabilities of modern smartphone cameras and augmented reality frameworks and tools
		like MediaPipe, this system eliminates the need for external hardware,
		such as tracking gloves or depth sensors, making it accessible and portable.
		The project explores the integration of OpenCV and MediaPipe for image processing and hand detection
		in a mixed reality application developed in Unity,
		and the possibility to involve depth-sensing technologies like LiDAR, Time-of-Flight
		and stereo vision sensors available in modern smartphones.
		By reproducing musical notes based on finger positioning in the physical world,
		the application offers an immersive, educational tool that combines music and technology.
		The study also discusses the system architecture, challenges in real-time hand tracking,
		and the potential future enhancements in the realm of mobile AR applications.
	\end{abstract}

	\begin{acknowledgments}[Ringraziamenti]
		Ringrazio la Fondazione TIM per aver supportato finanziariamente il progetto tramite l'iniziativa
		Call for IDEAs -- Inclusione Sociale, e la Fondazione Anna Maria Catalano per averci guidato
		durante tutte le fasi del concorso e per aver gestito la parte burocratica e sociale del progetto.
		\\
		Ringrazio il professor Luigi Cinque e Marco Raoul Marini per aver creduto per primi nel progetto,
		e per averci aperto le porte del VisionLab.
		\\
		Ringrazio tutti i ragazzi e le ragazze del VisionLab,
		che ci hanno fatto trovare un ambiente accogliente e amichevole oltre ogni aspettativa.
		\\
		Ringrazio Valerio Venanzi, il mio partner in questa avventura che è cominciata come
		l'ennesimo progetto di coppia da fare insieme per l'ennesimo esame.
	\end{acknowledgments}

	\input{introduction/introduction}

	\input{state-of-the-art/state-of-the-art}

	\input{architecture/architecture}

	\input{results/results}

	\input{conclusions/conclusions}

	\backmatter
	\cleardoublepage
	\phantomsection
	\addcontentsline{toc}{chapter}{\bibname}
	\bibliographystyle{sapthesis}
	\bibliography{bibliography}

\end{document}
